Full proof on the differential privacy property of $\hexpmech$

### 2018-10-23 notes/fullproof/main.tex
update proof

\begin{document}
\title{Tailoring Differentially Private Bayesian Inference to Distance Between Distributions}

\begin{abstract} Bayesian inference is a statistical method which
allows one to derive a \emph{posterior} distribution,
starting from a \emph{prior} distribution and observed data. Several
approaches have been explored in order to make this process differentially
private. For example, \citet{dimitrakakis2014robust}, and
\citet{wang2015privacy} proved that, under specific conditions, sampling from
the posterior distribution is already differentially private. \citet{zhang2016differential}, \citet{foulds2016theory},
designed differentially private mechanisms that output a
representation of the full posterior distribution.

When the output of a differentially private mechanism is a probability
distribution, accuracy is naturally measured by means of
\emph{probabilistic distances} measuring how far this distribution is
from the original one. Some classical examples are total variation distance,
Hellinger distance, $\chi^2$-distance, KL-divergence, etc.

In this work, we design a mechanism for
bayesian inference exploring the idea of calibrating noise using the
same probabilistic distance we want to measure accuracy with. 
We focus on two discrete models, the Beta-Binomial and the
Dirichlet-multinomial models, and one probability distance, Hellinger distance. 
Our mechanism can be understood as a version of  the exponential mechanism
where the noise is calibrated to the smooth sensitivity of the
utility function, rather than to its global sensitivity. In our
setting, the utility function is the probability distance we want to
use to measure accuracy. To show the usefulness of this mechanism we
show an experimental analysis comparing it with mechanisms based on
the Laplace mechanism.
\end{abstract}

@@

\section{Introduction}
\label{sec_intro}
Data analysis techniques are broadly used in various applications in different areas to improve their services, including disease-medicine service, financial service, location service, social network and so on. In order to provide a better service, large of data are collected from users for analysis. As a consequence, the data privacy came to be a critical issue. Sensitivity information in data can be revealed through the analysis results. The key challenge here is to release a private analysis results, from which adversary cannot observe individual's sensitive information in data.

Plenty of work have been developed to solve this issue, guaranteeing the privacy in specific data analysis algorithms. They achieved the $\epsilon-$differential privacy by adopting either Laplace mechanism or achieved the $(\epsilon, \delta)-$differential privacy. But they are not giving better accuracy than the differential privacy mechanism itself. Here, we are proposing mechanism with better accuracy.

Our work is conducted under a Bayesian inference scenario, where the posterior distribution is the analysis result we obtained from the data.
Publishing the posterior distribution inferred from a sensitive dataset can
leak information about the individuals in the dataset.
In order to guarantee differential privacy and to protect the
individuals' data we can add noise to the posterior before releasing it.
The amount of the noise that we need to introduced
depends on the privacy parameter $\epsilon$ and the sensitivity of the inference to
small changes in the data set. 
Sensitivity can be computed in many different ways based on which metric space
we consider on the output set of the mechanism. In the literature on private Bayesian
inference (\cite{zhang2016differential,xiao2012bayesian}), it is only measured with
respect to the vector of numbers parametrizing the output distribution using, e.g. the $\ell_1$ norm.
A more natural approach which we explore here, is to measure sensitivity with respect to a metric on the space of inferred probability distributions.
A re-loved question is that of how to measure accuracy. Again,
this can be answered in different ways based on the metric imposed on the output space, and yet again
only in few works in literature (e.g. \cite{zhang2016differential})
distances between probability measures have been used for these purposes.

The question that this work aims at answering is whether
an approach based on probability metrics can improve on the accuracy of approaches based on metrics over
the numeric parameters of the distributions. 
We will see that in some cases this can happen.

\noindent \textbf{Main contributions.}
\begin{itemize}
	\item We designed a differentially private Bayesian inference mechanism based on the standard exponential mechanism.
	\item The accuracy is improved by two ways: 1) calibrating noise to the sensitivity of a
         metric over distributions (e.g. Hellinger distance ($\hellinger$), $f$-divergences, etc\dots). 2) Using a smooth upper bound on the local sensitivity and scale the noise to this smooth bound rather than global sensitivity, to improve the mechanism accuracy.
	\item We implemented the new proposed mechanism and other art-of-state mechanisms, comparing the performance in terms of accuracy and efficiency.
\end{itemize}

\noindent \textbf{Related Work.}

A plentiful of data analysis algorithms have been studied to preserve differential privacy, including the subspace clustering algorithm \citet{wang2015differentially}, the gradient decedent algorithm in deep learning \citet{abadi2016deep}, logical regression \citet{chaudhuri2009privacy}, principle component analysis \citet{chaudhuri2012near}, probabilitic inference \citet{williams2010probabilistic} and convergence in statistic estimation \citet{chaudhuri2012convergence}, etc.

In Bayesian Inference data analysis, some algorithms have been studied and mechanisms proposed corresponded to maintain their differential privacy. There are 3 main topics: 1) Inherited differential privacy property of posterior sampling in Bayesian inference. \citet{dimitrakakis2014robust}, \citet{zhang2016differential}, \citet{zheng2015differential} and \citet{wang2015privacy}. 2) Data sampled and released from posterior distribution of Bayesian is differentially private \citet{Zhang2017privbayes}, \citet{dimitrakakis2015differential},  \citet{foulds2016theory}. 3) The inference process is differentially private and the posterior distribution released should be private itself. The third topic where our work focus on is still very new.

@@

\section{Technical Problem Statement and Motivations}
\label{sec_moti}
We are interested in designing a mechanism for privately releasing the full posterior
distributions derived in section \ref{sec_background}, as opposed to just sampling from them.
It's worth noticing that the posterior distributions are fully characterized
by their parameters, and the family (beta, Dirichlet) they belong to. Hence, in case of the
Beta-Binomial model we are interested in releasing a private version of the pair of
parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
in the case of the Dirichlet-multinomial model we are interested in a private version of
$\valpha'=(\valpha + \Delta \valpha)$. \citet{zhang2016differential} and \citet{xiao2012bayesian}
have already attacked this problem by adding independent Laplacian noise to the
parameters of the posteriors. That is, in the case of the Beta-Binomial system,
the value released would  be: $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$
where $\widetilde{\Delta \alpha}\sim \lap{\Delta \alpha}{\frac{2}{\epsilon}}$,
and where $\lap{\mu}{\nu}$ denotes a Laplace random variable with mean $\mu$ and scale $\nu$.
This mechanism is $\epsilon$-differentially private, and the noise is
calibrated w.r.t. to a sensitivity of 2 which is derived by using
$\ell_1$ norm over the pair of parameters. Indeed, considering two
adjacent\footnote{Given $\dataobs, \dataobs'$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff\\
$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } data observations
$\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
distributions, characterized by the pairs
$(\alpha',\beta')$ and $(\alpha'',\beta'')$ then
$|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
This argument extends similarly to the Dirichelet-Multinomial system. Details are introduced in Sec. \ref{subsec_baselines}.

However, in previous works, the accuracy of the posterior was measured again with respect to $\ell_1$ norm. That is, an upper bound was given on
\[
  \Pr[|\alpha - \tilde\alpha| + |\beta - \tilde\beta |\geq \gamma ]
\]
where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are as defined above. This accuracy metric is meaningless when the results released are distributions rather than numerical values. In contrast, distribution metrics such as $f$-divergence, Hellinger distance, etc. come into mind overtly when we are measuring distance between distributions. This gives us motivation on using a different norm (a distribution metric) to compute the sensitivity
and provide guarantees on the accuracy.

Specifically, we will use the Hellinger distance $\hellinger(\cdot,\cdot)$:
Given two beta distributions
$\boldsymbol{\beta}_1=\betad(\alpha_1, \beta_1),$ and $\boldsymbol{\beta}_2=\betad(\alpha_2, \beta_2)$ the following equality holds 
\[
  \hellinger(\boldsymbol{\beta}_1, \boldsymbol{\beta}_2)=
  \sqrt{1 - \frac{\betaf(\frac{\alpha_1 + \alpha_2}{2}, \frac{\beta_1 + \beta_2}{2})}{\sqrt{\betaf(\alpha_1,\beta_1)\betaf(\alpha_2,\beta_2)}}}
\]

Our choice to use Hellinger distance is motivated by three facts:
\begin{itemize}
\item It simplifies calculations in the case of the probabilistic models considered here.
\item It also automatically yields bounds on the total variation distance, which represents also the maximum advantage
an unbounded adversary can have in distingishing two distributions. 
\item The accuracy can be improved by using a smooth bound on Hellinger distance's local sensitivity. As shown in Fig. \ref{fig_sensitivity}, taking advantage of the gap between the global sensitivity and local sensitivity, we can improve the accuracy by applying a smooth upper bound on local sensitivity instead of using global sensitivity.
\begin{figure}[ht]
\centering
\includegraphics[width=0.35\textwidth]{sensitivity_2d.eps}
\caption{{Sensitivity of $\hellinger$}}
\label{fig_sensitivity}
\end{figure}
\end{itemize}

@@

\subsection{Baseline Mechanisms}
\label{subsec_baselines}
Baseline Mechanisms are introduced in prior to our mechanism: $\hexpmech$.

\subsubsection{Exponential Mechanism}
Exponential mechanism $\expmech{}{x}{u}{\candidateset}$ samples a element from the candidate set $\candidateset = \{r_1, r_2, \cdots r_n\}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 GS})$:
\begin{equation*}
\underset{z \thicksim \expmech{}{x}{u}{\candidateset} }{Pr}[z=r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 GS})}
{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 GS})},
\end{equation*}
where $u(x,r)$ is the Hellinger scoring function over candidates, $-\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity calculated by:
\begin{equation*}
GS = 
\max_{\{|\dataobs,\dataobs'| \leq 1;\dataobs,\dataobs'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}
|\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)|
\end{equation*}

Exponential mechanism is $\epsilon -$differential privacy\cite{dwork2014algorithmic}.

\subsubsection{Exponential Mechanism with Local Sensitivity}
\label{subsec_emls}
% \subsubsection{Mechanism Set up}
Exponential mechanism with local sensitivity $\expmech{local}{x}{u}{\candidateset}$ share the same candidate set and utility function as it with standard exponential mechanism. This outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 LS(x)})$:
\begin{equation*}
\underset{z \thicksim \expmech{local}{x}{u}{\candidateset}}{\Pr}[z=r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 LS(x)})}
{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 LS(x)})},
\end{equation*}

where $LS(x)$ is the local sensitivity calculated by:

\begin{equation*}
LS(\dataobs)=\max_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert.
\end{equation*}

The exponential mechanism with local sensitivity is non-differential privacy\cite{dwork2014algorithmic}.

\subsubsection{Baseline Mechanism - Laplace Mechanism}
 Adding noise to the posterior distribution parameters directly, through Laplace mechanism ($\lap{\cdot}{\cdot}$) with post-processing:

 \[
 \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
 \] 
 where $Y \sim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in Beta-binomial model; and
 \[
 \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
 \]
 where $Y_i \sim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in Dirichlet-multinomial model. $\lfloor \cdot \rfloor^n_0$ is taking the floor value and truncating into $[0,n]$ to make sure the noised posterior is valid.

 Then release it as the private posterior distribution.

 The sensitivity used in this baseline mechanism is:
 \[
 \Delta \bysinfer \equiv \max\limits_{\dataobs, \dataobs' \in \{0,1\}^{n}, ||\dataobs - \dataobs'||_1 \leq 1} ||\bysinfer(\dataobs) - \bysinfer(\dataobs')||_1,
 \]
 which is proportional to the dimensionality.

\subsubsection{Improved Laplace Mechanism}

 Noise added to posterior distribution parameters are scaled to smaller sensitivity in this improved Laplace mechanism. Because in terms of two adjacent data sets $\dataobs, \dataobs'$, their posterior distributions by Bayesian inference -- $\bysinfer(\dataobs), \bysinfer(\dataobs')$ -- which parameter differs at most in 2 dimensions even though extended to Dirichlet-multinomial mode, i.e., $\Delta \bysinfer \leq 2$.

 Then it is enough to use sensitivity $1$ in 2 dimensions and $2$ in higher dimensions:

 \[
 \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
 \]
 where $Y \sim \lap{0}{\frac{1}{\epsilon}}$ in Beta-binomial model; and
 \[
 \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
 \]
where $Y_i \sim \lap{0}{\frac{2}{\epsilon}}$ in Dirichlet-multinomial model.

Both Laplace mechanism and improved one are $\epsilon -$differential privacy\cite{dwork2014algorithmic}.

@@

\subsection{Privacy Analysis for Baseline Mechanisms}
In baseline mechanisms, \emph{exponential mechanism}, \emph{Laplace mechanism}, \emph{improved Laplace mechanism} are $\epsilon-$differential privacy provided by \citet{dwork2014algorithmic}. The \emph{exponential mechanism with local sensitivity} is non-differential privacy, also from \citet{dwork2014algorithmic}.

@@

In what follows, we will use a correspondence between the probability
 $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ of every
 $r\in\candidateset$ and the probability 
 $\underset{z \thicksim \hexpmech(x)}{Pr}[\hellinger(\bysinfer(x),z) =
 \hellinger(\bysinfer(x),r)]$ for the utility score for $r$. In Beta-binomial system, because of the property of beta function, the order of parameters in Beta distribution doesn't matter when computing the Hellinegr distance. More specifically, for 3 different beta distributions $\betad(\alpha_0, \beta_0)$, $\betad(\alpha_1, \beta_1)$ and $\betad(\alpha_2, \beta_2)$, $\hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_1, \beta_1)) = \hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_2, \beta_2))$ iff $\alpha_2 = \beta_1$,  $\alpha_1 = \beta_2$ and $\alpha_0 + \alpha_1 = \beta_0 + \beta_2$ and $\alpha_0 + \alpha_2 = \beta_0 + \beta_1$.

 From this, we can derive that there are either only one or two candidates in $\candidateset$ can have the same score, i.e., for every $r \in \candidateset$ we have: $
 \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ either 
 $$
 =\frac{1}{2}\Big (\underset{z \thicksim \hexpmech(x)}{Pr}[\hellinger(\bysinfer(x),z) =
 \hellinger(\bysinfer(x),r)]\Big )
 $$ or 
 $$
 =\underset{z \thicksim \hexpmech(x)}{Pr}[\hellinger(\bysinfer(x),z) = \hellinger(\bysinfer(x),r)]
 $$
 % proportional too $\hellinger(\bysinfer(x),r)$, i.e., $u(x,z)$. We can derive, if $u(r,x) = u(r',x)$ then $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(x)}{Pr}[z = r']$. 
 We assume the number of candidates $z \in \mathcal{R}$ that satisfy $\hellinger(\bysinfer(x),z) = \hellinger(\bysinfer(x),r)$, i.e. $u(z,x) = u(r,x)$ is $|z|$, then  $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = |z| \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$. It can be infer that $|z| = 2$ or $|z| = 1$, i.e., $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ or $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$.

 The same way in Dirichlet-multinomial system. By combination and permutation, $|z|$ can take value of 1 or 3 or 6 in 3 dimensionality, and trivially in higher dimensions.

 In Beta-binomial system, let $R_1, R_2 \subset \candidateset$ be a partition of $\candidateset$, where every $z \in R_1$ has a distinct score, i.e., $|z| = 1$ and $z \in R_2$ has another $z' \in R_2$ with the same score, i.e., $|z| = 2$. The proofs are given by parts:

 \begin{itemize}
 	\item for $r \in R_1$:

@@

		\begin{equation*}
		\begin{split}
		\frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)}}
		& \leq \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{\epsilon}{2}}\\
		&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] \leq RHS\\
		\end{split}
		\end{equation*}
	\item for $r \in R_2$: Actually is exactly the same as above by eliminating the parameter $|z|$ in both sides.
\end{itemize}

The same in Dirichlet-multinomial distribution, partitioning the $\candidateset$ by the possible value of $|z|$, the proof can be derived in the same way as above by part.

@@

\noindent \textbf{Dilation Property of $\hexpmech$}
\begin{lem}
for any exponential mechanism $\hexpmech(x)$, $\lambda < |\beta|$, $\epsilon$, $|\delta| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 |\candidateset|})})$, the dilation property holds:

\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = c]
\leq
e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta}{2},
\end{equation*}
where the sensitivity in mechanism is still smooth sensitivity as above.

More specifically, in Beta-binomial system it is enough to take $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$.
\end{lem}

\begin{proof}
We partition $\candidateset$ in the same way as before, $R_1, R_2$. It is enough to proof under just one partition. Without loss of generalization, we take $R_1$.

@@

We set the $h(c) = Pr[u(\hexpmech(x)) = c] = \frac{exp(\frac{\epsilon c}{2 S(x)})}{NL(x)}$.

@@

\textbf{Detail proof:}
	To show:
	\begin{equation*}
	\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = c]
	\leq
	e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta}{2}
	\end{equation*}
	for $z \in R_1$.

	Let $Pr[u(\hexpmech(x)) = c] = \frac{exp(\frac{\epsilon c}{2 S(x)})}{NL(x)}$ and $Pr[u(\hexpmech(x)) = e^{\lambda} c] = \frac{exp(\frac{\epsilon e^{\lambda} c}{2 S(x)})}{NL(x)}$ by definition.

	After simplification, we need to show: $u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}$.
	Because the sensitivity is always greater than 0, and our utility function $-\hellinger(\bysinfer(x),z)$ is smaller than zero, i.e., $u(z,x) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:

\begin{itemize}
	\item $\lambda < 0$

@@

For all neighboring $x, y \in D^n$ and all sets $\mathcal{S}$, we need to show that:
\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[ z = r] \leq e^{\epsilon} \underset{z \thicksim \hexpmech(y)}{Pr}[z = r] + \delta. 
\end{equation*}

Let partition $R_1, R_2 \subset \candidateset$ the same as above. Then we prove by part:
\begin{itemize}
	\item for $r \in R_1$:

	Given that $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(x)}{Pr}[u(x,z) = u(x,r)]$, let $U = u(x,r)$, $U_1 = u(y,z) - u(x,z)$, $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)})$. Then,

	\begin{equation*}
	\begin{split}
	\underset{z \thicksim \hexpmech(x)}{Pr}[ z = r]
	& = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = U]\\
	& \leq e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = U_2]\\
	& \leq e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = U_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\\
	& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(y)}{Pr}[ u(y,z) = U] + \frac{e^{\epsilon/2} \delta'}{2} \\
	& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ z = r] + \delta,
	\end{split}
	\end{equation*}
	where $\delta = \frac{e^{\epsilon/2} \delta'}{2}$.
	The first inequality holds by the sliding property, since the $U_1 \geq -S(x)$. The second inequality holds by the dilation property, since $\frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})}$.

	\item for $r \in R_2$:

	Given that $2\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]\Big) = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = u(x,r)]$, let $U = u(x,r)$, $U_1 = u(y,z) - u(x,z)$, $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)})$. Then,

	\begin{equation*}
	\begin{split}
	\underset{z \thicksim \hexpmech(x)}{Pr}[ z = r]
	& = 	\frac{1}{2}\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = U]\Big)\\
	& \leq 	\frac{1}{2}\Big( e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = U_2]\Big)\\
	& \leq 	\frac{1}{2}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = U_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\Big)\\
	& = 	\frac{1}{2}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(y)}{Pr}[ u(y,z) = U] + \frac{e^{\epsilon/2} \delta'}{2}\Big) \\
	& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ z = r] + \delta,
	\end{split}
	\end{equation*}
	where the $\delta = \frac{e^{\epsilon/2} \delta'}{4}$.

	The first inequality holds by the sliding property, since the $U_1 \geq -S(x)$. The second inequality holds by the dilation property, since $\frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})}$.
\end{itemize}

Based on two cases above, $\hexpmech$ is $(\epsilon, \delta)-$differential privacy, where $\delta$ takes the maximum value form the two cases.

Proof in Dirichlet-multinomial system can be derived in the same way by proving in parts and taking the maximum $\delta$ value of each part. 
\end{proof}

@@

\subsubsection{Accuracy Bound for Exponential Mechanism}
\label{subsec_accuracy_global}
The accuracy bound of exponential mechanism is provided in \cite{dwork2014algorithmic} as:
\begin{equation*}
Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
		 \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(x)}}{2 GS})},
\end{equation*}
where $|R|$ is the size of the candidate set, $OPT$ is the optimal candidates, $|R_{OPT}|$ is the number of optimal candidates.

\subsubsection{Accuracy Bound for Laplace Mechanism}
\label{subsec_accuracy_lap}
Accuracy bound for Laplace mechanism is provided by its probability density function:
\begin{equation*}
Pr[|Y| \geq t] = e^{- \frac{t}{b}},
\end{equation*}
where $Y \sim Lap(b)$, $b = \frac{\Delta \bysinfer}{\epsilon}$ in our case.

After post-processing, Laplace noise is discretized. Then the accuracy bound for Laplace mechanism is obtained by:
\[
Pr[\lfloor Y \rfloor = t] = Pr[ t-1 \leq Y < t] = \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t)}{\Delta \bysinfer}}).
\]

\subsubsection{Accuracy Bound for Improved Laplace Mechanism}
\label{subsec_accuracy_lap}
Accuracy bound for improved Laplace mechanism is obtained from the standard Laplace Mechanism by replacing the sensitivity of $\Delta \bysinfer$ with $2$.
\[
Pr[\lfloor Y \rfloor = t] = Pr[ t-1 \leq Y < t] = \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{2}} - e^{- \frac{\epsilon (t)}{2}}).
\]

@@

\section{Experimental Evaluations}
\label{sec_experiment}

\subsection{Computation Efficiency Optimization}
\label{subsec_effi}
The formula for computing the local sensitivity presented in Sec. \ref{subsec_baselines}: $LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert.$ 
can be reduced to $\max\limits_{\{|\dataobs,\dataobs'| \leq 1; \dataobs'\in \mathcal{X}^n\}}\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs'))|$
by applying the distance triangle property.

>>>>

\begin{document}
\title{Full proof on the differential privacy property of $\hexpmech$}

\begin{abstract}
\end{abstract}

@@

@@

@@

@@

@@

In what follows, we will use a correspondence between the probability
 $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ of every
 $r\in\candidateset$ and the probability 
 $\underset{z \thicksim \hexpmech(x)}{Pr}[\hellinger(\bysinfer(x),z) =
 \hellinger(\bysinfer(x),r)]$ for the utility score for $r$. In particular, for every
 $r\in\candidateset$ we have:

$$
\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]=
\frac{1}{2}\Big (\underset{z \thicksim \hexpmech(x)}{Pr}[\hellinger(\bysinfer(x),z) =
 \hellinger(\bysinfer(x),r)]\Big )
$$

To see this, it is enough to notice that: $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ is proportional too $\hellinger(\bysinfer(x),r)$, i.e., $u(x,z)$. We can derive, if $u(r,x) = u(r',x)$ then $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(x)}{Pr}[z = r']$. We assume the number of candidates $z \in \mathcal{R}$ that satisfy $u(z,x) = u(r,x)$ is $|r|$, we have  $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = |r| \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$. Because Hellinger distance  $\hellinger(\bysinfer(x),z)$ is axial symmetry, where the $\bysinfer(x)$ is the symmetry axis. It can be infer that $|z| = 2$ for any candidates, apart from the true output, i.e., $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$. This parameter can be eliminate in both sides in proof.

@@

\begin{equation*}
\begin{split}
\frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)}}
& \leq \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{\epsilon}{2}}\\
&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] \leq RHS\\
\end{split}
\end{equation*}

@@

\noindent \textbf{Dilation Property of $\hexpmech$}
\begin{lem}
for any exponential mechanism $\hexpmech(x)$, $\lambda < |\beta|$, $\epsilon$, $|\delta| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, the dilation property holds:

\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = c]
\leq
e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta}{2},
\end{equation*}
where the sensitivity in mechanism is still smooth sensitivity as above.
\end{lem}

@@

We set the $h(c) = Pr[u(\hexpmech(x)) = c] = 2\frac{exp(\frac{\epsilon z}{2 S(x)})}{NL(x)}$.

@@

\textbf{Detail proof:}

	By simplification, we get this formula: $u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}$
\begin{itemize}
	\item $\lambda < 0$

@@

\begin{proof}
of Lemma \ref{lem_hexpmech_privacy}: For all neighboring $x, y \in D^n$ and all sets $\mathcal{S}$, we need to show that:
\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}] \leq e^{\epsilon} \underset{z \thicksim \hexpmech(y)}{Pr}[z \in \mathcal{S}] + \delta. 
\end{equation*}
Given that $2\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}]\Big) = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}]$, let $\mathcal{U}_1 = \frac{u(y,z) - u(x,z)}{S(x)}$, $\mathcal{U}_2 = \mathcal{U} + \mathcal{U}_1$ and $\mathcal{U}_3 = \mathcal{U}_2 \cdot \frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)})$. Then,

\begin{equation*}
\begin{split}
2\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}]\Big)
& = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}]\\
& \leq e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}_2]\\
& \leq e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\\
& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(y)}{Pr}[ u(y,z) \in \mathcal{U}] + \delta = 2\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}] \Big) + \delta\\
\end{split}
\end{equation*}

The first inequality holds by the sliding property, since the $\mathcal{U}_1 \geq -S(x)$. The second inequality holds by the dilation property, since $\frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})}$.

@@

@@
